Data reduction for HGIS

### 2021-06-10 doc/hgis_data_reduction.Rmd
Fix external error.
knit to html
Fix blank error propagation eqn

---
title: "Data reduction for HGIS"
output: html_notebook
---

@@

$$ \sigma_{ext} = \sqrt{\frac{}} $$

@@

$$ \sigma_{cor} = \sqrt{\sigma_{norm}^2 * \frac{1 + R_{blank}}{R_{std}}^2 + \sigma_{blank}^2 * \frac{R_{norm}-R_{std}}{R_{std}}^2} $$

>>>>

---
title: "Data reduction for HGIS"
output:
  html_document:
    df_print: paged
---

@@

$$ \sigma_{ext} = \frac{SE(R_{cor})}{mean(R_{cor})}$$

@@

$$ \sigma_{cor} = \sqrt{\sigma_{norm}^2 * \left(\frac{1 + R_{blank}}{R_{std}}\right)^2 + \sigma_{blank}^2 * \left(\frac{R_{norm}-R_{std}}{R_{std}}\right)^2} $$
